\begin{abstract}
There is an increasing trend for automating warehouses and factories leveraging
on teams of autonomous robotic agents. The orchestration problem for a fleet of
autonomous robotic cooperating agents has been tackled in the literature as
Multi-Agent Path Finding (MAPF). Several algorithms have been proposed in the
literature to solve the MAPF problem. However, these algorithms have been only
applied to synthetic randomly generated scenarios. The application in real
scenarios demands scalability (being able to deal with realistic size
warehouses) and efficiency (being able to quickly adapt to changes in the
problems due, e.g., to new orders or change in the priorities). \newline
In this work we perform a detailed analysis of the MAPF literature, we selected
the most effective algorithms, we implemented them and we carried out an
experimental analysis on a real scalable warehouse of a large distribution
company to evaluate their applicability in such scenarios. \newline
The results show that a) there is not a clear winner; b) there are difficult
(realistic) cases out of the scope of all the algorithms. For such difficult
cases, we designed novel heuristics to be employed by the best algorithms to
solve them efficiently. 
\end{abstract}

\endinput
\begin{abstract}
The new industrial revolution is proving the critical role of robotics in
industry and also in everyday lives of people. This work focuses on the
Multi-Agent Path Finding (MAPF) considering a real warehouse located in the
center of Italy as the main scenario. \newline
First, we start with a description of the state-of-the-art algorithms
used to solve the Single-Agent Path Finding (SAPF) problem since they are used
as a building block for many algorithms solving the MAPF problem. After that we
move to a precise description of the algorithms that solve the main problem
showing their strengths and their weak spots. In particular, we focus on the
description of correct and optimal solvers. Next we propose a concise review of
some variants of the classical MAPF problem explaining why some of these
aspects are important to model our problem on the warehouse. Then, we describe
the three algorithms we have chosen and implemented to tackle the
aforementioned problem explaining the modification we had to make to them in
order to be used in our scenario. Two of these are based on the same MAPF
algorithm, but they use different internal solvers as it will be more clear
later on. Finally the third algorithm is based on constraint programming, which
differs from all the other implementations. \newline
After that, we also delineate a suite of tests taken from the warehouse map of
increasing difficulty. Next a discussion on the results and the future work
that may come with it is carried out. The results show the implemented
algorithms’ limitations, from the analysis of which we describe a particularly
difficult case. Eventually, we propose some modifications to the algorithms
that may improve the performance and the number of cases they manage to solve.
\end{abstract}
